
---
title: "Sales Forecasting Dashboard"

output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    runtime: shiny
---

```{r setup, include=FALSE}
# Set CRAN mirror
options(repos = c(CRAN = "https://cloud.r-project.org"))

# Install packages if not already installed
packages <- c("flexdashboard", "ggplot2", "shiny", "forecast", "tidyverse", "plotly")
new_packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages)

# Load libraries
library(flexdashboard)
library(ggplot2)
library(shiny)
library(forecast)
library(tidyverse)
library(plotly)
```

```{r loading, include=FALSE}
# Load data
fsales <- "https://raw.githubusercontent.com/multidis/hult-inter-bus-reports-r/main/forecasting/sales_weekly.csv"
sales <- read_csv(fsales)

# Ensure proper data formats
sales$Week <- as.integer(sales$Week)
sales$Store <- as.factor(sales$Store)

# Latest (current) week
nweek_now <- max(sales$Week)
```

### UI Elements

```{r ui_elements}
# Create store selection input
store_choices <- unique(sales$Store)

selectInput("store", "Select Store:",
            choices = store_choices, selected = store_choices[1])

# UI for forecasting options
selectInput("forecast_option", "Select Forecast Type:",
            choices = c("Quarterly Forecast" = "quarterly", "Weekly Forecast" = "weekly"))

# UI for quarter selection
quarter_input <- sliderInput("quarter", "Select Future Quarter:",
                             min = 1, max = 8, value = 1)

# UI for week selection
week_input <- sliderInput("week", "Select Week:",
                          min = nweek_now + 1, max = nweek_now + 13*3, value = nweek_now + 1)

# UI for confidence intervals
confidence_input <- sliderInput("confidence_interval", "Select Confidence Interval Level:",
                                min = 80, max = 95, value = 95, step = 5)

# UI for comparing past and future sales
comparison_input <- checkboxInput("compare_sales", "Compare Past and Future Sales", value = FALSE)
```

### Historical Sales Data and Current Week Performance

```{r historical_data}
# Reactive data based on selected store
filtered_sales <- reactive({
  req(input$store)
  subset(sales, Store == input$store)
})

# Current week performance indicator
current_week_sales <- reactive({
  latest_week_data <- subset(filtered_sales(), Week == nweek_now)
  forecast_model <- auto.arima(filtered_sales()$Weekly_Sales)
  current_week_forecast <- forecast(forecast_model, h = 1)$mean
  c(actual = latest_week_data$Weekly_Sales, forecast = current_week_forecast)
})
```

Row {data-height=650}
-------------------------------------

### Current Week Performance

```{r current_week_performance}
# Display current week performance indicator
renderTable({
  data <- current_week_sales()
  data.frame(
    Metric = c("Actual Sales", "Forecast Sales"),
    Value = c(data["actual"], data["forecast"])
  )
})
```

### Historical Sales Data Table

```{r historical_table}
# Display historical sales data table
renderTable({
  filtered_sales()
})
```

### Historical Sales Chart

```{r historical_chart}
# Display historical sales chart
renderPlot({
  data <- filtered_sales()
  ggplot(data, aes(x = Week, y = Weekly_Sales)) +
    geom_line() +
    geom_point() +
    labs(title = paste("Weekly Sales for Store", input$store),
         x = "Week", y = "Weekly Sales")
})
```

### Sales Forecasting

```{r forecasting}
# Generate forecast based on selected options
output$forecast_chart <- renderPlot({
  req(input$store)
  store_data <- filtered_sales()
  
  forecast_result <- NULL
  if (input$forecast_option == "quarterly") {
    quarter_end <- nweek_now + (input$quarter * 13)
    forecast_data <- subset(store_data, Week >= nweek_now & Week <= quarter_end)
    if (nrow(forecast_data) > 1) {
      forecast_model <- auto.arima(forecast_data$Weekly_Sales)
      forecast_result <- forecast(forecast_model, h = 13 * input$quarter)
      autoplot(forecast_result) +
        labs(title = paste("Quarterly Sales Forecast for Store", input$store),
             x = "Week", y = "Forecasted Sales")
    } else {
      plot(1, type = "n", xlab = "Week", ylab = "Forecasted Sales",
           main = "Insufficient Data for Forecast")
    }
  } else if (input$forecast_option == "weekly") {
    forecast_week <- input$week
    forecast_data <- subset(store_data, Week <= forecast_week)
    if (nrow(forecast_data) > 1) {
      forecast_model <- auto.arima(forecast_data$Weekly_Sales)
      forecast_result <- forecast(forecast_model, h = 1)
      autoplot(forecast_result) +
        labs(title = paste("Weekly Sales Forecast for Store", input$store),
             x = "Week", y = "Forecasted Sales")
    } else {
      plot(1, type = "n", xlab = "Week", ylab = "Forecasted Sales",
           main = "Insufficient Data for Forecast")
    }
  }
})
```

### Forecast with Confidence Intervals

```{r confidence_intervals}
output$confidence_chart <- renderPlot({
  req(input$store)
  
  store_data <- filtered_sales()
  forecast_model <- auto.arima(store_data$Weekly_Sales)
  forecast_result <- forecast(forecast_model, h = 4 * 13) # Forecast for 4 months
  
  ggplot(forecast_result) +
    autoplot() +
    labs(title = paste("Sales Forecast with Confidence Intervals for Store", input$store),
         x = "Week", y = "Forecasted Sales") +
    geom_ribbon(aes(ymin = `80%`, ymax = `95%`), alpha = 0.2, fill = "blue")
})
```

### Comparison of Past and Future Sales

```{r comparison_sales}
output$comparison_chart <- renderPlot({
  req(input$store, input$compare_sales)
  
  store_data <- filtered_sales()
  forecast_model <- auto.arima(store_data$Weekly_Sales)
  forecast_result <- forecast(forecast_model, h = 52)  # Forecast for 1 year
  
  past_data <- store_data %>%
    filter(Week >= (nweek_now - 52)) %>%
    mutate(Type = "Past Sales")
  
  future_data <- data.frame(
    Week = (nweek_now + 1):(nweek_now + 52),
    Weekly_Sales = forecast_result$mean,
    Type = "Forecast Sales"
  )
  
  combined_data <- rbind(past_data, future_data)
  
  ggplot(combined_data, aes(x = Week, y = Weekly_Sales, color = Type)) +
    geom_line() +
    labs(title = paste("Comparison of Past and Future Sales for Store", input$store),
         x = "Week", y = "Sales")
})
```

Este código cria um `flexdashboard` interativo com as seguintes funcionalidades personalizadas:
- **Indicador de Desempenho da Semana Atual**: Mostra as vendas reais e a previsão para a semana atual.
- **Previsão para o Futuro**: Permite selecionar a previsão para um trimestre futuro ou uma semana específica.
- **Intervalos de Confiança**: Exibe a previsão com intervalos de confiança para o próximo mês.
- **Comparação de Vendas**: Compara as vendas semanais do ano passado com as previsões para o próximo ano.

Coloque este código em um arquivo `.Rmd` e execute-o no RStudio para gerar o dashboard interativo.